---
title: "ScRNA-Seq"
author: "Chris Doan"
date: "2022-07-16"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(Seurat)
library(ggplot2)
library(tidyverse)
library(gridExtra)
```


```{r read_file}
dirs <- list.dirs(path = 'intergrate_sc_RNA_Seq_data', recursive = F, full.names = F)

mtx_obj_s5 <- ReadMtx(mtx = 'GSE137015_RAW/S5_filtered_gene_bc_matrices/matrix.mtx',
        features = 'GSE137015_RAW/S5_filtered_gene_bc_matrices/genes.tsv',
        cells = 'GSE137015_RAW/S5_filtered_gene_bc_matrices/barcodes.tsv')
seurat_mtx_s5 <- CreateSeuratObject(counts = mtx_obj_s5, project = 'CT', min.cells = 5)
seurat_mtx_s5[['percent.mt']] <- PercentageFeatureSet(seurat_mtx_s5, pattern = '^mt-')

seurat_mtx_s5 <- subset(seurat_mtx_s5, subset = nCount_RNA < 40000 & 
                                   nFeature_RNA > 500 &
                                   percent.mt <5)

seurat_mtx_s5 <- NormalizeData(object = seurat_mtx_s5)
seurat_mtx_s5 <- FindVariableFeatures(object = seurat_mtx_s5)

```


```{r pressure, echo=FALSE}
FeatureScatter(seurat_mtx_s5, feature1 = 'nCount_RNA',feature2 = 'nFeature_RNA') +
  geom_smooth(method = 'lm')
```

```{r}
VlnPlot(seurat_mtx_s5, features = c('nFeature_RNA','nCount_RNA','percent.mt'), ncol = 3) +
  geom_smooth(method = 'lm')

```

```{r}
mtx_obj_s6 <- ReadMtx(mtx = 'GSE137015_RAW/S6_filtered_gene_bc_matrices/matrix.mtx',
                   features = 'GSE137015_RAW/S6_filtered_gene_bc_matrices/genes.tsv',
                   cells = 'GSE137015_RAW/S6_filtered_gene_bc_matrices/barcodes.tsv')
seurat_mtx_s6 <- CreateSeuratObject(counts = mtx_obj_s6, project = 'CT', min.cells = 5)
seurat_mtx_s6[['percent.mt']] <- PercentageFeatureSet(seurat_mtx_s6, pattern = '^mt-')
seurat_mtx_s6 <- subset(seurat_mtx_s6, subset = nCount_RNA < 40000 & 
                                   nFeature_RNA > 500 &
                                   percent.mt <5)

seurat_mtx_s6 <- NormalizeData(object = seurat_mtx_s6)
seurat_mtx_s6 <- FindVariableFeatures(object = seurat_mtx_s6)
```

```{r}
VlnPlot(seurat_mtx_s6, features = c('nFeature_RNA','nCount_RNA','percent.mt'), ncol = 3) +
  geom_smooth(method = 'lm')
```

```{r}
mtx_obj_s7 <- ReadMtx(mtx = 'GSE137015_RAW/S7_filtered_gene_bc_matrices/matrix.mtx',
                   features = 'GSE137015_RAW/S7_filtered_gene_bc_matrices/genes.tsv',
                   cells = 'GSE137015_RAW/S7_filtered_gene_bc_matrices/barcodes.tsv')
seurat_mtx_s7 <- CreateSeuratObject(counts = mtx_obj_s7, project = 'CT', min.cells = 5)
seurat_mtx_s7[['percent.mt']] <- PercentageFeatureSet(seurat_mtx_s7, pattern = '^mt-')
seurat_mtx_s7 <- subset(seurat_mtx_s7, subset = nCount_RNA < 40000 & 
                          nFeature_RNA > 500 &
                          percent.mt <5)

seurat_mtx_s7 <- NormalizeData(object = seurat_mtx_s7)
seurat_mtx_s7 <- FindVariableFeatures(object = seurat_mtx_s7)
```

```{r}
mtx_obj_s8 <- ReadMtx(mtx = 'GSE137015_RAW/S8_filtered_gene_bc_matrices/matrix.mtx',
                   features = 'GSE137015_RAW/S8_filtered_gene_bc_matrices/genes.tsv',
                   cells = 'GSE137015_RAW/S8_filtered_gene_bc_matrices/barcodes.tsv')
seurat_mtx_s8 <- CreateSeuratObject(counts = mtx_obj_s8, project = 'CT', min.cells = 5)
seurat_mtx_s8[['percent.mt']] <- PercentageFeatureSet(seurat_mtx_s8, pattern = '^mt-')
seurat_mtx_s8 <- NormalizeData(object = seurat_mtx_s8)
seurat_mtx_s8 <- FindVariableFeatures(object = seurat_mtx_s8)
```

```{r}
merged_seurat <- merge(seurat_mtx_s5, y = c(seurat_mtx_s6, seurat_mtx_s7, seurat_mtx_s8),
                       add.cell.ids = c('s5','s6','s7','s8'),
                       project = 'CT')
```

```{r}
merged_seurat$sample <- rownames(merged_seurat@meta.data)
merged_seurat@meta.data <- separate(merged_seurat@meta.data, col = 'sample', into = c('cell_types','Barcode'),
                                    sep = '_')
merged_seurat[['percent.mt']] <- PercentageFeatureSet(merged_seurat, pattern = '^mt-')

merged_seurat_filtered <- subset(merged_seurat, subset = nCount_RNA < 40000 & 
                          nFeature_RNA > 500 &
                          percent.mt <5)

```


```{r}
merged_seurat_filtered <- NormalizeData(object = merged_seurat_filtered)
merged_seurat_filtered <- FindVariableFeatures(object = merged_seurat_filtered)
merged_seurat_filtered <- ScaleData(object = merged_seurat_filtered)
merged_seurat_filtered <- RunPCA(object = merged_seurat_filtered)
ElbowPlot(merged_seurat_filtered)
merged_seurat_filtered <- FindNeighbors(object = merged_seurat_filtered, dims = 1:20)
merged_seurat_filtered <- FindClusters(object = merged_seurat_filtered)
merged_seurat_filtered <- RunUMAP(object = merged_seurat_filtered, dims = 1:20)
```

```{r}
p1 <- DimPlot(merged_seurat_filtered, reduction = 'umap', group.by = 'cell_types')
p2 <- DimPlot(merged_seurat_filtered, reduction = "umap", label = TRUE, repel = TRUE)
p1 + p2
```

```{r}
obj.list1 <- SplitObject(merged_seurat_filtered, split.by = 'cell_types')
```

```{r}
features <- SelectIntegrationFeatures(object.list = obj.list1)

features <- SelectIntegrationFeatures(object.list = c(seurat_mtx_s5,seurat_mtx_s6,seurat_mtx_s7,seurat_mtx_s8))
anchors <- FindIntegrationAnchors(object.list = obj.list1,
                       anchor.features = features)

```

```{r}
seurat.integrated <- IntegrateData(anchorset = anchors)
seurat.integrated <- ScaleData(object = seurat.integrated)
seurat.integrated <- RunPCA(object = seurat.integrated)
seurat.integrated <- RunUMAP(object = seurat.integrated, dims = 1:50)
```

```{r}
p5 <- DimPlot(seurat.integrated, reduction = 'umap', group.by = 'cell_types')
p6 <- DimPlot(merged_seurat_filtered, reduction = "umap", label = TRUE, repel = TRUE)
p5+p6
```

```{r}
immune.anchors <- FindIntegrationAnchors(object.list = c(seurat_mtx_s5,seurat_mtx_s6,seurat_mtx_s7,seurat_mtx_s8),anchor.features = features)

immune.combined <- IntegrateData(anchorset = anchors)

immune.combined$sample <- rownames(immune.combined@meta.data)
immune.combined@meta.data <- separate(immune.combined@meta.data, col = 'sample', into = c('cell_types','Barcode'),
                                    sep = '_')
DefaultAssay(immune.combined) <- "integrated"
```

```{r}
immune.combined <- ScaleData(immune.combined, verbose = FALSE)
immune.combined <- RunPCA(immune.combined, npcs = 30, verbose = FALSE)
immune.combined <- RunUMAP(immune.combined, reduction = "pca", dims = 1:30)
immune.combined <- FindNeighbors(immune.combined, reduction = "pca", dims = 1:30)
immune.combined <- FindClusters(immune.combined, resolution = 0.5)
```

```{r}
DefaultAssay(immune.combined) <- "RNA"

```

```{r}
FeaturePlot(immune.combined, features = c("Pdcd1", "Havcr2", "Gzmb", "Id2", "Batf", "Ifng"
                                          ), min.cutoff = "q9")
```

## Biological conclusions:

After checking quality control, all samples are good for downstream analysis.
We have samples from wild-type and knock-out cells so I perform scRNA-Seq integration.

Cells from s5 and s6 have similar sources of variation, and cells from s7 and s8 have similar sources of variation. 
The algorithms identify a total of 15 clusters of cells. 
Cells from s8 samples have the highest sources of variation.
Many cells from s7 and s8 samples separate from s5 and s6 samples.

From FeaturePlot genes of interest (Pdcd1, Havcr2, Gzmb, Id2, Batf, Ifng), we see different expression levels of these marker genes in all cells from wild-type and knockouts cells. Gzmb gene has the expression level highest.
